---
title: 'RMarkdown:  In Class Assignment'
author: "Alexander Park"
date: "Data 2401"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) ## this line makes all the code show! 
  ## and these lines are comments - anything behind a '#' doesn't run!
```


Reminder: There is a "Markdown Help" page available in RStudio. 


## In-class Activity, Markdown

Below the "Your work here" section header, do the following 3 things. To turn this in, knit the RMarkdown file, and zip and submit the html.  

1. Make a subsection called "Wise words". Put your favorite quote in a block quote. Add a functioning link to a website that provides more information about that quote.

### Wise Words

> 
```
"Stand up and walk. Keep moving forward. You've got two good legs. So get up and use them. You're strong enough to make your own path.-Edward Elric"
```
[link](https://www.goodreads.com/quotes/802053-stand-up-and-walk-keep-mo       ving-forward-you-ve-got-two#:~:text=You've%20got%20two%20good,%2DEdward%       20Elric%E2%80%9D) 


2. Make a subsection called "My semester". Make a three column table of the current courses you are taking, with separate columns for course number (put those in __bold__), course title (put those in _italics_), and instructor name.

#### My Semester 

 __CS 1311__ |  __DATA 2401__ | __MATH 2402__
------------- | -------------|-------------
  _Intro to Python and Computer Science_| _Data Science I_ | _Calculus II_
 John Henderson | Jocye Hallaway| Katherine Shoemaker




3. Lastly, make subsection called "I recommend", and add some information about your favorite author or musician.

#### I recommend 

##### Portor Robinson 

```{r}
("Don't try to make yourself remember darling
Don't look for me I'm just a story you've been told
So let's pretend a little longer
Cause when we're gone
Everything goes on")
```

 __List of Songs Performed__
 
1. Shelter 
2. Sad Machine
3. Look at the Sky 
4. Something Comforting 
5. Blossom
6. Goodbye To A World
7. Mother 
8. Mirror 
9. Trying to Feel Alive
10. SWeet Time



+ A _subsubheading_ with the name of the artist or author;    
+ An example of their writing or lyrics (formatted in a *plain code block*);   
+ A _list_ of things they have written or performed (remember to use the formatting markup for a list!).     


Note that you can click "Knit" as you go along to see what the final results are going to look like. **Once you're done, commit the changes and push the repo back to your assignment on GitHub!**
 
